### 2024-02-05 README.Rmd
remove refs to older name
remove duplication

# sfislands <img src="man/figures/logo.png" align="right" height="120"/>

@@

You can install the development version of `kh` from [GitHub](https://github.com/) with:

>>>>

<img src="man/figures/logo.png" align="right" height="240"/>

@@

You can install the development version of `sfislands` from [GitHub](https://github.com/horankev/sfislands) with:
